metric analysis

### 2021-05-30 metric_analysis.Rmd
Fix met-metric plots

library(readr)
resist <- read_csv("ED-outputs/results/metric/resistance_values.csv")
met <- read_csv("ED-outputs/results/constant_annual_met_data.csv")
```

@@

library(tidyr)
met2_wide <- pivot_wider(met2, id_cols = "met", names_from = "variable")
pca_met <- prcomp(met2_wide[-1], scale. = TRUE)
biplot(pca_met, scale = 0)
pairs(met2_wide[-1])
```

@@

```{r}
ggplot(resist, aes(trough_resistance, fill = severity)) +
  geom_histogram(bins = 20) + 
  facet_wrap(~variable)
```

@@

```{r, fig.height=8}
# Build a combined met-metric dataset
resist %>% 
  select(variable, met, trough_resistance) %>% 
  # We see from the met analysis above that vbdsf and vddsf are highly
  # correlated with nbdsf and nddsf respectively; remove one pair
  left_join(select(met2_wide, -nbdsf, -nddsf), by = "met") ->
  resist_combined

resist_combined %>% 
  pivot_longer(dlwrf:vgrd) %>% 
  ggplot(aes(trough_resistance, value, color = variable)) +
  geom_point() + 
  facet_wrap(variable~name, scales = "free_y") + 
  geom_smooth(method = "lm", formula = y ~ x) +
  theme(legend.position = "none", axis.text = element_text(size = 5))
```

>>>>

library(readr)
resistance <- read_csv("ED-outputs/results/metric/resistance_values.csv")
resilience <- read_csv("ED-outputs/results/metric/resilience_values.csv")
met <- read_csv("ED-outputs/results/constant_annual_met_data.csv")
```

@@

library(tidyr)
met2_wide <- pivot_wider(met2, id_cols = "met", names_from = "variable")
pca_met <- prcomp(met2_wide[-1], scale. = TRUE)  # -1 removes met year column 
biplot(pca_met, scale = 0)
pairs(met2_wide[-1])
```

@@

```{r}
ggplot(resistance, aes(trough_resistance, fill = severity)) +
  geom_histogram(bins = 20) + 
  ggtitle("Resistance") +
  facet_wrap(~variable)

ggplot(resilience, aes(resilience, fill = severity)) +
  geom_histogram(bins = 20) + 
  ggtitle("Resilience") +
  facet_wrap(~variable)
```

@@

```{r, fig.height=8}
# Build a combined met-metric dataset
resistance %>% 
  select(variable, met, trough_resistance) %>% 
  # We see from the met analysis above that vbdsf and vddsf are highly
  # correlated with nbdsf and nddsf respectively; remove one pair
  left_join(select(met2_wide, -nbdsf, -nddsf), by = "met") ->
  resist_combined

resist_combined %>% 
  pivot_longer(dlwrf:vgrd) %>% 
  ggplot(aes(value, trough_resistance, color = variable)) +
  geom_point() + 
  facet_wrap(variable~name, scales = "free") + 
  geom_smooth(method = "lm", formula = y ~ x, color = "black", linetype = 5) +
  theme(legend.position = "none", axis.text = element_text(size = 5))
```
